Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-26 Tex/Old text/chapters/appendix.tex
Thesis update

%\textbf{List of Publications}
%
\section{List of Publications}
Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.

\subsection{Journals}

@@

\subsection{Congress}
Trindade, A., Cordeiro, L. \textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}. This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.

\section{Tools Description and How to Use it}

In this section, we describe the two tools created during the PhD process to implement and test the two scientific methodologies of the thesis.

\subsection{Tools}

\subsection{How to use it}

>>>>

%\textbf{List of Publications}
%
Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.

\section{Journals}

@@

\section{Congress}

Trindade, A., Cordeiro, L. \textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}. This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.

### 2019-10-26 Tex/Old text/chapters/conclusion.tex
Thesis update

At this final chapter, we present the conclusions about the research done during the Doctoral process. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable source) closes the work.

@@

This Thesis contributions can be split in two, each one concerning the techniques proposed with the use of model checking to solar PV systems, and the tools created to validate it.

It was described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$. Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system. In addition, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.

Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

It was described and evaluated as well, an automated synthesis method to obtain the optimal size of PV system using software model checking techniques. It was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results. The automated synthesis tool presented detailed optimal solution to six case studies adopted in this paper, with specifications, models, and the arrangement in terms of series-parallel connections, thereby covering the charge controller, which was not presented by HOMER Pro. In a nutshell, the proposed automated synthesis tool took more time to find the optimal solution than HOMER Pro; however, the presented solution was more complete and detailed, which is very useful to a user to get a list of equipment and go to shopping.

@@

And last, but not least important to report, besides the fact that the goal of a PhD is to make a contribution to the body of human research, one of the great things about PhD is you will be able to conduct your own research. In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and even smart grids, or electrical systems in general. Few research has been made until now, and the scenario is auspicious from now on.

>>>>

At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were applied to solar PV systems. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.

@@

Our contributions can be split in two, each one concerning the scientific methods proposed with the use of model checking to solar PV systems, and the tools created to validate it.

Related to the first contributions, depicted with details in ~\autoref{chap:automatedverification}, it was described and evaluated an automated verification method to validate over the time a given stand-alone PV system design, and see if it meets its user and electrical requirements using software model checking techniques. There are a lot of possibilities to perform that validation, as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal); however, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from interview if the owners, that our approach is feasible and effective.

It was considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W (inverter specification); and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method that we proposed takes longer than simulation methods, it is able to avoid the battery bank oversize produced by the simulation tool in houses $1$, $2$, $3$, and $4$. This result was validated by the sized systems deployed at the field.

Moreover, it was not necessary to 'adapt' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order to not perform the optimization of the system. In addition, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

Furthermore, we have also contributions from the method depicted in ~\autoref{chap:automatedsynthesis}. We have described and evaluated an automated synthesis method to obtain the optimal size of the PV system using software model checking techniques. The focus was on the synthesis method to obtain the optimal solution based on formal methods, which can cover better the design-space as opposed to simulation tools. Our thesis produced a methodological research with innovative value regarding the first use of automated synthesis for optimal sizing of solar PV systems.

We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis. Our algorithm, that implements the method, uses a data base of commercial equipment from the marketing, including the price. In order to validate the method, it was considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) in order to compare the results. In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.

In summary, our synthesis proposal is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro. In particular, our method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current, and voltage; we also cover the charge controller, which is unavailable in HOMER Pro. Note that our automated synthesis tool took longer to find the optimal solution than HOMER Pro; however, the presented solution is sound and complete; it also provides a list of equipment to be bought from manufacturers. %Moreover, we extended the CEGIS synthesis method and implemented this extension within our proposed formal synthesis tool, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis.

@@

And last, but not least important to report, besides the fact that the goal of a PhD is to make a contribution to the body of human research, one of the great things about PhD is you will be able to conduct your own research. In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there is a vast field of future applications and developments, using different renewable sources, as biomass, as wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general. Few research has been made until now, and the scenario is auspicious from now on.

### 2019-10-26 Tex/Old text/chapters/introduction.tex
Thesis update

% ~\nameref or \autoref{
Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling. Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique. Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork. Chapter '~\nameref{chap:conclusions}' presents the main contributions, future work directions and concluding remarks.

>>>>

% ~\nameref or \autoref{
Chapter '~\nameref{chap:background}' gives the theoretical basis on formal methods, formal verification, automated verification, solar PV systems, design and validation of PV systems, program synthesis, and the mathematical modeling.

Chapter '~\nameref{chap:automatedverification}' presents the automated formal verification technique, the experimentation details, and the results obtained with the tool created using this new technique.

Chapter '~\nameref{chap:automatedsynthesis}' presents the automated synthesis technique from computer science applied to solar PV systems, with details of the experimentation, and the results using the tools created to compare this new technique with simulation tool and from data collect during fieldwork.

Chapter '~\nameref{chap:conclusions}' presents the main contributions, future work directions and concluding remarks.

~\autoref{chap:publications} presents a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.

~\autoref{chap:tools} depicts the tools created during the PhD process to implement and validate the two scientific methods of the thesis (and how to use it).
